\documentclass[12pt,letterpaper]{scrreprt}
\begin{document}


\chapter{Container Classes}
	\section{AttackerStack}
	Data Types
	\begin{itemize}
		\item AttackerType: list of entity classes present in the stack.\
		\item AttackDifferential: dictionary for to hit and damage lookup based on the entities in the stack.\
		\item AttackModifier: list of attack modifiers collected from entity Possessions or Special abilities.\
		\item CurrentRound: integer keeping track of the current round, to assist with updating the AttackModifier list and DefenseModifier list.
	\end{itemize}
	Methods
	\begin{itemize}
		\item Attack/Capture/ApplyWounds: update the state of the game via the server through bidirectional communication.
		\item UpdateCombatRating/UpdateModifiers: perform server queries to determine new to hit and damage modifiers for lookup in the AttackDifferential dictionary.
	\end{itemize}
	\section{DefenderStack}
	Data Types
	\begin{itemize}
		\item DefenderType: list of entity classes present in the stack.
		\item DefenseDifferential: dictionary for to hit and damage lookup based on the entities in the stack.
		\item DefenseModifier: list of attack modifiers collected from entity Possessions and or environ bonuses
Methods.
		\item Retaliate/BreakOff/Inactive/ApplyWounds: update the state of the game via the server through bidirectional communication.
		\item UpdateCombatRating: perform server queries to determine new to hit and damage modifiers for lookup in the DefenseDifferential dictionary.
	\end{itemize}
	\section{MissionGroupStack}
	Data Types
	\begin{itemize}
		\item EffectiveCombatRating: the combat rating minus wounds for all characters present in the mission group.
		\item BonusDraws: list of integers for the applicable bonus draws characters receive for attempting certain kinds of missions.
	\end{itemize}
	Methods
	\begin{itemize}
 		\item various methods will probably be needed to effectively request and update information on the server regarding the state of the characters present in the MissionGroupStack.
	\end{itemize}
	\section{MissionDeck}
	\begin{itemize}
 		\item contain sate information regarding the available Missions.
	\end{itemize}
	\section{PossessionDeck}
	\begin{itemize}
 		\item contain state information regarding the available Possessions.
	\end{itemize}
\chapter{Entity Classes}
	\section{Military Unit}
	\section{IrateLocals}
	Methods
	\begin{itemize}
		\item GetType: determines the type of IrateLocal or Creature based upon a given environ.
	\end{itemize}
	\section{Creature}
		Methods
		\begin{itemize}
			\item GetSpecial: determines the available Speicals given the creature by performing a server query.
		\end{itemize}
	\section{Character}
	\section{MissionGroup}
		\begin{itemize}
 			\item refer to the information above
 		\end{itemize}
\chapter{Misc Classes}
	\section{Possession}
	\section{Ship}
	\section{Companion}
	\section{Mission}
\end{document}
